Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-12 icmssp-paper/appendix.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

This integral can be approximated using the five-point Gauss--Legendre quadrature rule \cite{kythe_quadrature_2002}. We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
\end{align*}
Then, we approximate the integral using the following summation:
\begin{align*}
  \int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
	\end{align*}
	\columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
	\end{align*}
\end{multicols}
Applying this procedure to the integral in equation \ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) \approx
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}

While the closed form approximation in equation \ref{eq:standardquadrature} is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in figure \ref{fig:standardquadrature}.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}

@@

Figure \ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$. Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately $0.0103315865985758$, occurring at $x=255$. This is an improvement from the approximation in equation \ref{eq:standardquadrature}, which has a maximum absolute error of $1.19717868468392$, similarly occurring at $x=255$.

\begin{figure}[h]
    \centering
    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
    \label{fig:scaledquadrature}
\end{figure}

\subsection{Approximation for $x^\gamma$}
To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
\end{align*}

This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}

>>>>

This integral can be approximated using the five-point Gauss--Legendre quadrature rule \cite{kythe_quadrature_2002}. We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
\end{align*}
Then, we approximate the integral using the following summation:
\begin{align*}
  \int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
	\end{align*}
	% \columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
	\end{align*}
\end{multicols}

Applying this procedure to the integral in Equation~\ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) \approx
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}

% \pgfplotsset{
% 	every axis legend/.append style={anchor=south east},
% }

While the closed form approximation in Equation~\ref{eq:standardquadrature} is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in Figure~\ref{fig:standardquadrature}.
% \begin{figure}[!ht]
%     \centering
%     \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
%     \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
%     \label{fig:standardquadrature}
% \end{figure}
\begin{figure}[!ht]
    \centering
	\begin{tikzpicture}
		\begin{axis}[
			% height=6cm, width=9cm,
			xmin=0, xmax=300,
			ymin=0, ymax=5.5, ytick={0,...,6},
			xlabel={$x$}, ylabel={$y$},
			grid=major,
			legend pos=south east,
			legend cell align=left,
		]
		\addplot[very thick, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
		\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
		\legend{5-point quadrature approximation, Actual value of $\log(1+x)$}
		\end{axis}
	\end{tikzpicture}%
    \caption{Graph of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}

@@

Figure~\ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$. Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately $0.0103315865985758$, occurring at $x=255$. This is an improvement from the approximation in Equation~\ref{eq:standardquadrature}, which has a maximum absolute error of $1.19717868468392$, similarly occurring at $x=255$.

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
%     \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
%     \label{fig:scaledquadrature}
% \end{figure}
\begin{figure}[h]
    \centering
    \begin{tikzpicture}
		\begin{axis}[
			% height=6cm, width=9cm,
			xmin=0, xmax=300,
			ymin=0, ymax=0.04,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[thick, domain=0:300, samples=100]{abs((1/30*(137*x^5 + 33185*x^4 + 931370*x^3 - 13403630*x^2 - 289469315*x - 713567363)/(x^5 + 505*x^4 + 42010*x^3 + 923010*x^2 + 5722005*x + 8040501))-ln((1/20)+(1/20)*x))};
		\end{axis}
	\end{tikzpicture}%
    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:scaledquadrature}}
    \label{fig:scaledquadrature}
\end{figure}

\subsection{Approximation for $x^\gamma$}
\label{sec:approx-pwr}
To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
\end{align*}

This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow \quad e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}

### 2019-03-12 icmssp-paper/icmssp2019-sigconf.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

%Conference
% \acmConference[PCSC2019]{Philippine Computing Science Congress}{March 2019}{City of Manila, Philippines}
% \acmYear{2019}
\CopyrightYear{2019}

@@

\numberofauthors{2}
\author{
\alignauthor Aldrich Ellis C. Asuncion\\
\affaddr{Ateneo de Manila University}\\
\affaddr{Katipunan Avenue, Loyola Heights}\\
\affaddr{Quezon City, Philippines}\\
\email{aldrich.asuncion@obf.ateneo.edu}
\alignauthor Brian Christopher T. Guadalupe\\
\affaddr{Ateneo de Manila University}\\
\affaddr{Katipunan Avenue, Loyola Heights}\\
\affaddr{Quezon City, Philippines}\\
\email{brian.guadalupe@obf.ateneo.edu}
}

@@

\begin{abstract}
Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations. Preliminary results have shown that the Paillier and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
\end{abstract}

>>>>

%Conference
% \acmConference[PCSC2019]{Philippine Computing Science Congress}{March 2019}{City of Manila, Philippines}
% \acmYear{2019}
\doi{http://dx.doi.org/10.1145/12345.67890}
\CopyrightYear{2019}

@@

\numberofauthors{3}
\author{
\alignauthor Aldrich Ellis C. Asuncion\\
\affaddr{Ateneo de Manila University}\\
% \affaddr{Katipunan Ave., Loyola Heights}\\
\affaddr{Quezon City, Philippines}\\
\email{aldrich.asuncion@obf.\linebreak[0]ateneo.edu}
\alignauthor Brian Christopher T. Guadalupe\\
\affaddr{Ateneo de Manila University}\\
% \affaddr{Katipunan Ave., Loyola Heights}\\
\affaddr{Quezon City, Philippines}\\
\email{brian.guadalupe@obf.\linebreak[0]ateneo.edu}
\alignauthor William Emmanuel S. Yu\\
\affaddr{Ateneo de Manila University}\\
% \affaddr{Katipunan Ave., Loyola Heights}\\
\affaddr{Quezon City, Philippines}\\
\email{wyu@ateneo.edu}
}

@@

\begin{abstract}
Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations. Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
\end{abstract}
